Standartox: Standardising toxicity data

### 2020-04-06 article/article.tex
Updates from Overleaf

\begin{table}[H]
    \caption{R-packages used for the compilation of the Standartox database.}
    \label{tab:rpackages}
    \centering
\begin{tabular}{cc}
    \toprule
    \textbf{Title} & \textbf{Citation} \\ 
    \midrule
    devtools: Tools to Make Developing R Packages Easier & \citep{wickham_devtools_2019} \\
    RCurl: General Network HTTP FTP Client Interface for R & \citep{lang_rcurl_2020} \\
    stringr: Simple Consistent Wrappers for Common String Operations & \citep{wickham_stringr_2019} \\
    R: Various Programming Utilities & \citep{bengtsson_r_2019} \\
    udunits: Udunits 2 Bindings for R & \citep{hiebert_udunits_2016} \\
    rvest: Easily Harvest Scrape Web Pages & \citep{wickham_rvest_2019} \\
    httr: Tools for Working with URLs and HTTP & \citep{wickham_httr_2019} \\
    The: A Practical and Consistent Mapping Between JSON Data and R Objects & \citep{ooms_the_2014} \\
    readxl: Read Excel Files & \citep{wickham_readxl_2019} \\
    openxlsx: Read Write and Edit xlsx Files & \citep{schauberger_openxlsx_2019} \\
    purrr: Functional Programming Tools & \citep{henry_purrr_2019} \\ data: Extension of data frame & \citep{dowle_data_2019} \\
    RPostgreSQL: R Interface to the PostgreSQL Database System & \citep{conway_rpostgresql_2017} \\ DBI: R Database Interface & \citep{b_dbi_2019} \\
    vegan: Community Ecology Package & \citep{oksanen_vegan_2019} \\ The: NA & \citep{wickham_the_2011} \\
    outliers: Tests for outliers & \citep{komsta_outliers_2011} \\ feather: R Bindings to the Feather API & \citep{wickham_feather_2019} \\
    ggplot: Elegant Graphics for Data Analysis & \citep{wickham_ggplot_2016} \\ ggrepel: Automatically Position Non Overlapping Text Labels with & \citep{slowikowski_ggrepel_2019} \\
    ggridges: Ridgeline Plots in ggplot2 & \citep{wilke_ggridges_2018} \\
    scales: Scale Functions for Visualization & \citep{wickham_scales_2019} \\ treemapify: Draw Treemaps in ggplot2 & \citep{wilkins_treemapify_2019} \\ cowplot: Streamlined Plot Theme and Plot Annotations for ggplot2 & \citep{wilke_cowplot_2019} \\
    RColorBrewer: ColorBrewer Palettes & \citep{neuwirth_rcolorbrewer_2014} \\ treemap: Treemap Visualization & \citep{tennekes_treemap_2017} \\ rgbif: Interface to the Global Biodiversity Information Facility API & \citep{chamberlain_rgbif_2020} \\
    taxize: NA & \citep{chamberlain_taxize_2013} \\ countrycode: An R package to convert country names and country codes & \citep{bundock_countrycode_2018} \\ foreach: Provides Foreach Looping Construct for R & \citep{microsoft_foreach_2017} \\
    doParallel: Foreach Parallel Adaptor for the parallel Package & \citep{corporation_doparallel_2018} \\
    fst: Lightning Fast Serialization of Data Frames for R & \citep{klik_fst_2019} \\
    DT: A Wrapper of the JavaScript Library DataTables & \citep{xie_dt_2019} \\
    knitr: A General Purpose Package for Dynamic Report Generation in R & \citep{xie_knitr_2020} \\
    \bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}[H]
    \caption{R-packages used for the compilation of the Standartox database.}
    \label{tab:rpackages}
    \centering
\begin{tabular}{ccc}
\toprule
\textbf{Package} & \textbf{Description} & \textbf{Citation} \\ 
\midrule
bib2df & Parse a BibTeX File to a Data Frame & \citep{R-bib2df} \\
countrycode & Convert Country Names and Country Codes & \citep{R-countrycode} \\
cowplot & Streamlined Plot Theme and Plot Annotations for 'ggplot2' & \citep{R-cowplot} \\
data.table & Extension of `data.frame` & \citep{R-data.table} \\
DBI & R Database Interface & \citep{R-DBI} \\
dbreport & Automated reports from tables & \citep{R-dbreport} \\
devtools & Tools to Make Developing R Packages Easier & \citep{R-devtools} \\
doParallel & Foreach Parallel Adaptor for the 'parallel' Package & \citep{R-doParallel} \\
DT & A Wrapper of the JavaScript Library 'DataTables' & \citep{R-DT} \\
foreach & Provides Foreach Looping Construct for R & \citep{R-foreach} \\
fst & Lightning Fast Serialization of Data Frames for R & \citep{R-fst} \\
ggplot2 & Create Elegant Data Visualisations Using the Grammar of Graphics & \citep{R-ggplot2} \\ httr & Tools for Working with URLs and HTTP & \citep{R-httr} \\
jsonlite & A Robust, High Performance JSON Parser and Generator for R & \citep{R-jsonlite} \\
knitr & A General-Purpose Package for Dynamic Report Generation in R & \citep{R-knitr} \\
openxlsx & Read, Write and Edit xlsx Files & \citep{R-openxlsx} \\
plotly & Create Interactive Web Graphics via 'plotly.js' & \citep{R-plotly} \\
plumber & An API Generator for R & \citep{R-plumber} \\
R.utils & Various Programming Utilities & \citep{R-R.utils} \\
RColorBrewer & ColorBrewer Palettes & \citep{R-RColorBrewer} \\
reactlog & Reactivity Visualizer for 'shiny' & \citep{R-reactlog} \\
readxl & Read Excel Files & \citep{R-readxl} \\
rgbif & Interface to the Global 'Biodiversity' Information Facility API & \citep{R-rgbif} \\ RPostgreSQL & R Interface to the 'PostgreSQL' Database System & \citep{R-RPostgreSQL} \\
rvest & Easily Harvest (Scrape) Web Pages & \citep{R-rvest} \\
scales & Scale Functions for Visualization & \citep{R-scales} \\
shiny & Web Application Framework for R & \citep{R-shiny} \\
shinydashboard & Create Dashboards with 'Shiny' & \citep{R-shinydashboard} \\
shinydashboardPlus & Add More 'AdminLTE2' Components to 'shinydashboard' & \citep{R-shinydashboardPlus} \\
shinyjs & Easily Improve the User Experience of Your Shiny Apps in Seconds & \citep{R-shinyjs} \\ shinyWidgets & Custom Inputs Widgets for Shiny & \citep{R-shinyWidgets} \\
stringi & Character String Processing Facilities & \citep{R-stringi} \\
stringr & Simple, Consistent Wrappers for Common String Operations & \citep{R-stringr} \\
taxize & Taxonomic Information from Around the Web & \citep{R-taxize} \\
treemap & Treemap Visualization & \citep{R-treemap} \\
treemapify & Draw Treemaps in 'ggplot2' & \citep{R-treemapify} \\
udunits2 & Udunits-2 Bindings for R & \citep{R-udunits2} \\
webchem & Chemical Information from the Web & \citep{R-webchem} \\
\bottomrule
\end{tabular}
\end{table}
